### 2014-10-02 tex/precise.tex
Finished FW is deterministic

\begin{definition}
\label{def:ST}
The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
constraint from the reference $r$ with $\phi^\prime$ and keeps only location-constraint
pairs that are satisfiable after this strengthening:
\[
\begin{array}{rcl} 
\mathbb{ST}(L,r,\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ l) \mid  \\
& & \ \ \ \ (\phi^\prime\ l)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
\end{array}
\]
\end{definition}

>>>>

\begin{definition}
\label{def:ST}
The strengthen function $\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g)$ strengthens every
constraint from the reference $\cfgnt{r}$ with $\phi$ and keeps only location-constraint
pairs that are satisfiable after this strengthening with the inclusion of the global heap constraint $\phi_g$:
\[
\begin{array}{rcl} 
\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid  \\
& & \ \ \ \ (\phi^\prime\ \cfgnt{l}^\prime)\in \cfgnt{L}(\cfgnt{r})\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
\end{array}
\]
\end{definition}

### 2014-10-02 tex/proofs.tex
Finished FW is deterministic

\lemref{lem:S-mutex} establishes that the heap coming out of the
$S$-relation is deterministic, so it is only needed to show that
determinism is preserved by the call to the value function,
$\mathbb{VS}$, in the rule.

Recall from \defref{def:VS} that each constraint in each member of the value set has the form
$(\phi\wedge \phi^\prime\ l)$. Choose any two distinct members of the value set, $(\phi_\alpha \wedge
\phi_\alpha^\prime\ l_\alpha^\prime)$ and $(\phi_\beta \wedge
\phi_\beta^\prime\ l_\beta^\prime)$.
\begin{itemize}
\item If $\phi_\alpha = \phi_\beta$, then by \defref{lem:S-mutex} 
\[\begin{array}{l}
\exists (\phi_\alpha\ \cfgnt{l}) \in \cfgnt{L}(\cfgnt{r})\ (\exists \cfgnt{r}^\prime \in \cfgnt{R}(\cfgnt{l},\cfgnt{f})\ (\\
\ \ \ \ (\phi_\alpha^\prime\ l_\alpha^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime) \wedge (\phi_\beta^\prime\ l_\beta^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime)))
\end{array}
\]
As $(\phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and $(\phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$ are distinct and connected to the same reference $\cfgnt{r}^\prime$ in a deterministic heap, $\phi_\alpha^\prime \wedge  \phi_\beta^\prime = \cfgt{false}$ by definition.
\item If $\phi_\alpha \ne \phi_\beta$, then by \defref{lem:S-mutex} 
\[\begin{array}{l}
\exists \cfgnt{l}\ ((\phi_\alpha\ \cfgnt{l}) \in \cfgnt{L}(\cfgnt{r}) \wedge \exists \cfgnt{l}^\prime \neq \cfgnt{l} \ ((\phi_\beta\ \cfgnt{l}^\prime) \in \cfgnt{L}(\cfgnt{r})))
\end{array}
\]
As $(\phi_\alpha\ \cfgnt{l})$ and $(\phi_\beta\ \cfgnt{l}^\prime)$ are distinct and connected to the same reference $\cfgnt{r}$ in a deterministic heap, $\phi_\alpha \wedge  \phi_\beta = \cfgt{false}$ by definition.
\end{itemize}
The only change to the heap after the $S$-relation is the
addition of the new reference $\cfgnt{r}^\prime$ to point to the value
set. As the value set meets the conditions for determinism, the new heap $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
\mathrm{heap}(s_\varsigma^\prime)$ is also deterministic.
\end{proof}

>>>>

\lemref{lem:S-mutex} establishes that the heap coming out of the
$S$-relation is deterministic, so it is only needed to show that
determinism is preserved by the call to the value function,
$\mathbb{VS}$, in the rule. Let $(\cfgnt{L}\ \cfgnt{R})$ be that new
deterministic heap.

Recall from \defref{def:VS} that each constraint in each member of the value set has the form
$(\phi\wedge \phi^\prime\ \cfgnt{l})$. Choose any two distinct members of the value set, $(\phi_\alpha \wedge
\phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and $(\phi_\beta \wedge
\phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$.
\begin{itemize}
\item If $\phi_\alpha = \phi_\beta$, then by \defref{def:VS} 
\[\begin{array}{l}
\exists (\phi_\alpha\ \cfgnt{l}) \in \cfgnt{L}(\cfgnt{r})\ (\exists \cfgnt{r}^\prime \in \cfgnt{R}(\cfgnt{l},\cfgnt{f})\ (\\
\ \ \ \ (\phi_\alpha^\prime\ l_\alpha^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime) \wedge (\phi_\beta^\prime\ l_\beta^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime)))
\end{array}
\]
As $(\phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and $(\phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$ are distinct and connected to the same reference $\cfgnt{r}^\prime$ in a deterministic heap, $\phi_\alpha^\prime \wedge  \phi_\beta^\prime = \cfgt{false}$ by definition.
\item If $\phi_\alpha \ne \phi_\beta$, then by \defref{def:VS} 
\[\begin{array}{l}
\exists \cfgnt{l}\ ((\phi_\alpha\ \cfgnt{l}) \in \cfgnt{L}(\cfgnt{r}) \wedge \exists \cfgnt{l}^\prime \neq \cfgnt{l} \ ((\phi_\beta\ \cfgnt{l}^\prime) \in \cfgnt{L}(\cfgnt{r})))
\end{array}
\]
As $(\phi_\alpha\ \cfgnt{l})$ and $(\phi_\beta\ \cfgnt{l}^\prime)$ are distinct and connected to the same reference $\cfgnt{r}$ in a deterministic heap, $\phi_\alpha \wedge  \phi_\beta = \cfgt{false}$ by definition.
\end{itemize}
The only change to the heap after the $S$-relation is the
addition of the new reference $\cfgnt{r}^\prime$ to point to the value
set. As the value set meets the conditions for determinism, the new heap, $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
\mathrm{heap}(s_\varsigma^\prime)$, is also deterministic.
\end{proof}

\begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
\label{lem:FW-mutex}
Given a state, $s_\varsigma$, with a deterministic heap,
$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
\mathrm{heap}(s_\varsigma)$, the new heap,
$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the field
write rule, $s_\varsigma \rightarrow_\mathit{FW} s_\varsigma^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:sym}.

The $\rightarrow_\mathit{FW}$ rule relies on the $\mathbb{ST}$
function. Recall from \defref{def:ST} that each constraint in each
member of the strengthened set has the form $(\phi\wedge
\phi^\prime\ \cfgnt{l}^\prime)$ where every member,
$(\phi^\prime\ \cfgnt{l}^\prime)$, comes from
$\cfgnt{L}_\varsigma(\cfgnt{r})$ on the same reference in a
deterministic heap $(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma)$; thus,
that set of meets the criteria for determinism by definition. So any
application of $\mathbb{ST}$ preserves that criteria for determinism.

The $\rightarrow_\mathit{FW}$ makes two uses of the $\mathbb{ST}$
function, $\theta = \mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) \cup
\mathbb{ST}(\cfgnt{L},\cfgnt{r}_\mathit{cur},\neg\phi,\phi_g)$, to
build individual $\theta$ sets. Choose any two distinct members of $\theta$,
$(\phi_\alpha \wedge \phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and
$(\phi_\beta \wedge \phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$.
\begin{itemize}
\item If $\phi_\alpha = \phi_\beta$, then the constraints came from the
  same call to $\mathbb{ST}$ so $\phi_\alpha^\prime \wedge
  \phi_\beta^\prime = \cfgt{false}$ by definition.
\item If $\phi_\alpha \ne \phi_\beta$, then the constraints came from
  the different calls and are distinguished by the phase of $\phi$ in
  the call so $\phi_\alpha \wedge \phi_\beta = \cfgt{false}$.
\end{itemize}
Each $\theta$ is mapped to a new reference from
$\mathrm{fresh}_r()$. These are added to an already deterministic heap
$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma)$ and meet the criteria so
that $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime)$ is also
deterministic.
\end{proof}
